Open Policing Project Tutorial

### 2019-03-12 tutorial.Rmd

For the stop rate benchmark, what we really want to know is what the true 
distribution is for individuals breaking traffic laws or exhibiting other 
criminal behavior in their vehicles. If black and Hispanic drivers are
disproportionately stopped relative to their rates of offending, that would be
stronger evidence. Some people then proposed to use benchmarks that approximate
those offending rates, like arrests, for example. However, we know arrests to
themselves be racially skewed (especially for low-level drug offenses, for
example), so it wouldn't give us the true offending population's racial
distribution. Furthermore, only `stops %>% summarize(p = round(100 *
mean(arrest_made), 1)) %>% pull(p)`% of stops result in an arrest, so the
arrested population will naturally not match the stopped population.

>>>>

For the stop rate benchmark, what we really want to know is what the true 
distribution is for individuals breaking traffic laws or exhibiting other 
criminal behavior in their vehicles. If black and Hispanic drivers are
disproportionately stopped relative to their rates of offending, that would be
stronger evidence. Some people then proposed to use benchmarks that approximate
those offending rates, like arrests, for example. However, we know arrests to
themselves be racially skewed (especially for low-level drug offenses, for
example), so it wouldn't give us the true offending population's racial
distribution. Furthermore, only `r stops %>% summarize(p = round(100 *
mean(arrest_made), 1)) %>% pull(p)`% of stops result in an arrest, so the
arrested population will naturally not match the stopped population.
